List of build related FAQs.

\begin{itemize}

\item[] {\bf What's the minimum requirements to install LArLite?}
  \begin{itemize}
    \item See Sec.\ref{sec:prerequisite}.
  \end{itemize}

\item[] {\bf I installed \ROOT from macport. Can I still use LArLite?}
  \begin{itemize}
    \item Certainly. When you run {\ttfamily config/setup.sh}, it may
      complain that you do not have {\ttfamily \$ROOTSYS} set if you use
      release v2.1.1 or earlier. A walk around is to set {\ttfamily \$ROOTSYS}
      to some non-zero value and re-run the configuration script. Note that,
      in such case, you should set {\ttfamily \$PYTHONPATH} by yourself to
      use \PyROOT (if you want to use \PyROOT).
  \end{itemize}

\item[] {\bf I own OSX version above 10.6 but I don't have \clang. What do I miss?}
  \begin{itemize}
    \item If you do not have \clang, unless you installed additional tools 
      by yourself, you miss {\ttfamily c++11} feature. Contact the author 
      and educate him otherwise!
    \item One solution is to upgrade your system to OSX 10.9 Mavericks and
      install Xcode 5.X. The author found Xcode 5.X is fine for code
      development.
    \item Another solution is to install either (1) install {\ttfamily lldb}
      and \clang version above 3.1 (above 3.5 recommended), or (2)
      install \gpp version above 4.3 (above 4.6 recommended). Contact      
      the author for help / further assistance to enable {\ttfamily c++11}
      in LArLite compilation.      
  \end{itemize}

\item[] {\bf Can I use OSX 10.5 or earlier with {\ttfamily c++11} support?}
  \begin{itemize}
    \item The author tested it is possible on 10.5.8 with Xcode 3.1.4. Earlier
      version than this one is not tested. If you wish, please contact the author
      and he will be willing to help.
    \item The point is to have either recent-enough version of {\ttfamily lldb} 
      or \gpp. For \gpp, {\ttfamily c++11} features are added from 4.3 (and later
      versions have more features). The author took another choice and installed
      {\ttfamily lldb} 3.1 with \clang 3.1. This was successful but took 5 hours 
      to compile {\ttfamily lldb} 3.1 on his Core 2 duo from 2007.
  \end{itemize}

\item[] {\bf I have one of OSX 10.6, 10.7, or 10.8 with Xcode 4.X and seeing issues. Help?}
  \begin{itemize}
    \item Sure! The author does not have those machines and cannot test. So your
      help will be essential to support those OS versions. Make sure you have Xcode 4.2
      and up: this seems to be necessary to have \clang. Please contact the author.
  \end{itemize}

\item[] {\bf I think I installed LArLite. How can I test?}
  \begin{itemize}
    \item There are some test routines. See Sec.\ref{sec:simpletest}.
  \end{itemize}

\item[] {\bf How can I install \PyROOT? Do I need to re-compile LArLite?}
  \begin{itemize}
    \item See Sec.\ref{sec:pyroothelp} for a help on installation. No, you do not need to re-compile LArLite.
  \end{itemize}

\item[] {\bf Is there a class index list, like \ROOT web page?}
  \begin{itemize}
    \item You can generate your own \HTML file of class index. See Sec.\ref{sec:gendoxygen}.
  \end{itemize}

\end{itemize}



